Methodology for Assessing the State of the Practice for Domain X

### 2021-10-20 StateOfPractice/Methodology/Methodology.tex
Revisions to "Interaction with Domain Experts" section

As mentioned in the introduction (Section~\ref{SecIntroduction}), the Domain
Expert is an important member of the state of the practice assessment team.
Pitfalls exist if non-domain experts attempt to acquire an authoritative list of
software, or perform a commonality analysis or try to rank the software. The
main source of problems for non-domain experts is that they can only rely on
information that is available on-line, but on-line data has two potential
problems:
\begin{inparaenum}[i)]
  \item the on-line resources could have false or inaccurate information; and,
  \item the on-line resources could leave out relevant information that is so
in-grained with experts that nobody thinks to explicitly record the information.
\end{inparaenum}

Domain experts may be recruited from academia or industry.  The only
requirements are knowledge of the domain and a willingness to be engaged in the
assessment process.  The Domain Expert does not have to be a software developer,
but they should be a user of domain software.  Given that the domain experts are
likely to be busy people, the measurement process needs to benefit from their
expertise, without putting too much of a burden on their time.

>>>>

As mentioned in the introduction (Section~\ref{SecIntroduction}), the Domain
Expert is an important member of the state of the practice assessment team.
Pitfalls exist if non-domain experts attempt to acquire an authoritative list of
software, or perform a commonality analysis, or try to definitively rank the
software. The main source of problems for non-domain experts is that they can
only rely on information that is available on-line, but on-line data has two
potential problems:
\begin{inparaenum}[i)]
  \item the on-line resources could have false or inaccurate information; and,
  \item the on-line resources could leave out relevant information that is so
in-grained with experts that nobody thinks to explicitly record the information.
\end{inparaenum}

Domain experts may be recruited from academia or industry.  The only
requirements are knowledge of the domain and a willingness to be engaged in the
assessment process.  The Domain Expert does not have to be a software developer,
but they should be a user of domain software.  Given that the domain experts are
likely to be busy people, the measurement process cannot put to much of a burden
on their time.
